Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-13 mtjournal.tex
mari's notes on conclusion

\section{Conclusion}
\label{sec:conclusion}
In this research, we explore dependency pair match (DPM) a family of
syntactically-oriented measures.  Through a corpus of human judgments,
we settle on EDPM, a member of that family with promising predictive
power.  When tested against correlations with HTER, we find that EDPM
is as good a predictor of HTER as current measures BLEU$_4$ and TER,
and --- depending on the language and genre --- often better.

Several areas of future work are open to us. Using these syntactic
techniques may be possible as a late-pass evaluation, to identify how
candidate translation systems are performing overall.  Alternatively,
the various tree-decompositions of the DPM family could be used as
system diagnostics, by looking at relative quality of these component
scores compared to those of an alternative candidate system.

Another interesting research area is in the quality of the parser.  In
this work, we demonstrated that the
\inlinecite{charniak-johnson:2005:ACL} PCFG parser could serve in
place of the LFG parser used in
\inlinecite{owczarzak07labelleddepseval}. PCFG parsers, however, are
fairly easily adaptable to another domain. One interesting research
direction explores the intersection of genre (and genre-mismatch),
parser quality, and prediction of human performance. Another
consideration is the speed of the parser: parse time currently takes
much, much longer than BLEU, TER, or other word-based measures. We are
interested in the trade-offs --- if any --- among parse quality,
speed, and predictive power as a translation metric.  One possibility,
for example, is to store packed forests \cite{huang08packedforests}
rather than generating an $n$-best list only to sum across it again in
calculating the expectation.

>>>>

\section{Conclusion}
\label{sec:conclusion}
In this research, we explore dependency pair match (DPM) a family of
syntactically-oriented measures.  Through a corpus of human judgments,
we settle on EDPM, a member of that family with promising predictive
power.  We find that EDPM is superior to BLEU and TER in terms of
correlation with human judgments and as a per-document and
per-sentence predictor of HTER (using mean-subtraction to account for
underlying document- and segment-level difficulty).
% TO DO:  add something here regarding summary of tuning?

Several areas of future work are open to us. One obstacle to using
this method widely is the computational expense of the system. Parsing
is many times more computationally costly than word-based measures
such as BLEU or TER.  Using these syntactic
techniques may be possible as a late-pass evaluation, to identify how
candidate translation systems are performing overall.  Alternatively,
the various tree-decompositions of the DPM family could be used as
system diagnostics, by looking at relative quality of these component
scores compared to those of an alternative candidate system.

Another interesting research area is in the quality of the parser.  In
this work, we demonstrated that the
\inlinecite{charniak-johnson:2005:ACL} PCFG parser could serve in
place of the LFG parser used in
\inlinecite{owczarzak07labelleddepseval}. PCFG parsers, however, are
fairly easily adaptable to another domain. One interesting research
direction explores the intersection of genre (and genre-mismatch),
parser quality, and prediction of human performance. 
% Another
% consideration is the speed of the parser: parse time currently takes
% much, much longer than BLEU, TER, or other word-based measures. 
We are
interested in the trade-offs --- if any --- among parse quality,
speed, and predictive power as a translation metric.  One possibility,
for example, is to store packed forests \cite{huang08packedforests}
rather than generating an $n$-best list only to sum across it again in
calculating the expectation.
